Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
moving authors back to original order

\author{Daniel S.\ Katz$^{(1)}$,
Sou-Cheng T.\ Choi$^{(2)}$,
Kyle E.\ Niemeyer$^{(3)}$,
James Hetherington$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R.\ Brandt$^{(5)}$,
Mark A.\ Miller$^{(8)}$,
Sandra Gesing$^{(9)}$,
Nick D.\ Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Suresh Marru$^{(12)}$,
Gabrielle Allen$^{(13)}$,
Birgit~Penzenstadler$^{(14)}$,
Colin C.\ Venters$^{(15)}$,
Ethan Davis$^{(16)}$,
Lorraine Hwang$^{(17)}$,
Ilian~Todorov$^{(18)}$,
Abani Patra$^{(19)}$,
Miguel de Val-Borro$^{(20)}$
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(3)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ \hspace{-1.5ex}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ University of Washington, Seattle, WA, USA; nmweber@uw.edu}
%
\thanks{{}$^{(12)}$ Indiana University, Bloomington, IN, USA; smarru@iu.edu}
%
\thanks{{}$^{(13)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(14)}$ College of Computer Engineering \& Computer Science, California State University, Long Beach, CA, USA; birgit.penzenstadler@csulb.edu}
%
\thanks{{}$^{(15)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; c.venters@hud.ac.uk}
%
\thanks{{}$^{(16)}$ UCAR Unidata, Boulder, CO, USA; edavis@ucar.edu}
%
\thanks{{}$^{(17)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(18)}$ Science \& Technology Facilities Council, UK; ilian.todorov@stfc.ac.uk}
%
\thanks{{}$^{(19)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(20)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; valborro@princeton.edu}
%

>>>>

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sou-Cheng T.\ Choi$^{(3)}$,
James Hetherington$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R.\ Brandt$^{(5)}$,
Mark A.\ Miller$^{(8)}$,
Sandra Gesing$^{(9)}$,
Nick D.\ Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Suresh Marru$^{(12)}$,
Gabrielle Allen$^{(13)}$,
Birgit~Penzenstadler$^{(14)}$,
Colin C.\ Venters$^{(15)}$,
Ethan Davis$^{(16)}$,
Lorraine Hwang$^{(17)}$,
Ilian~Todorov$^{(18)}$,
Abani Patra$^{(19)}$,
Miguel de Val-Borro$^{(20)}$
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ \hspace{-1.5ex}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ University of Washington, Seattle, WA, USA; nmweber@uw.edu}
%
\thanks{{}$^{(12)}$ Indiana University, Bloomington, IN, USA; smarru@iu.edu}
%
\thanks{{}$^{(13)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(14)}$ College of Computer Engineering \& Computer Science, California State University, Long Beach, CA, USA; birgit.penzenstadler@csulb.edu}
%
\thanks{{}$^{(15)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; c.venters@hud.ac.uk}
%
\thanks{{}$^{(16)}$ UCAR Unidata, Boulder, CO, USA; edavis@ucar.edu}
%
\thanks{{}$^{(17)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(18)}$ Science \& Technology Facilities Council, UK; ilian.todorov@stfc.ac.uk}
%
\thanks{{}$^{(19)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(20)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; valborro@princeton.edu}
%
